Bootstrapping Domain Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-09 paper.tex
tiny edits to intro

Viewed as an inference problem,
our goal is to infer the DSL, written $\mathcal{D}$,
along with a program (written $p$) for each set of inputs/outputs (\emph{tasks}, written $x$).
A DSL $\mathcal{D}$ is a collection of domain specific subroutines.
We equip $\mathcal{D}$ with a real-valued weight vector, $\theta$, and together
$(\mathcal{D},\theta)$ define a distribution over programs.
Fig.~\ref{graphicalModel}(a) the diagrams this inference problem as a hierarchical Bayesian model.
Inference in this model is
difficult because the programs are unobserved,
and so we must solve a hard search problem to recover them. To make
search tractable we learn a bottom-up \emph{recognition
  model}, written $q(\cdot )$
(Fig.~\ref{graphicalModel}b).  The recognition model $q$ is a neural
network that regresses from input/output pairs to a distribution over
programs likely to explain the input/outputs. $q(\cdot )$ implements an amortized
inference
scheme~\cite{le2016inference} for the generative %ritchie2016deep
model.

>>>>

Viewed as an inference problem,
our goal is to infer the DSL (written $\mathcal{D}$)
along with a program (written $p$) for each set of inputs/outputs (\emph{tasks}, written $x$).
A DSL $\mathcal{D}$ is a collection of domain specific subroutines.
We equip $\mathcal{D}$ with a real-valued weight vector, $\theta$, and together
$(\mathcal{D},\theta)$ define a distribution over programs.
Fig.~\ref{graphicalModel}(a) diagrams this inference problem as a hierarchical Bayesian model.
Inference in this model is
difficult because the programs are unobserved,
and so we must solve a hard search problem to recover them. To make
search tractable we learn a bottom-up \emph{recognition
  model} (written $q(\cdot )$, Fig.~\ref{graphicalModel}(b)).
The recognition model $q$ is a neural
network that regresses from input/output pairs to a distribution over
programs likely to explain the input/outputs. $q(\cdot )$ implements an amortized
inference
scheme~\cite{le2016inference} for the generative %ritchie2016deep
model.
